Soss

### 2019-12-22 paper/paper.tex
Just some writing

\begin{abstract}
Abstract goes here
\end{abstract}

@@

@@

\todo[inline]{Can Soss really generate arbitrary code?}
The ability to generate arbitrary  Julia code makes it difficult to measure performance in Soss. When a performance bottleneck is found, developers or users can ask Soss to generate something different. This design places no a priori constraints on performance.

@@

\emph{Gen} \cite{Cusumano-Towner:2019}

@@

\section{Appendices}

>>>>

\begin{abstract}
Soss is a Julia-based embedded probabilistic programming language.
\end{abstract}

@@

\section{Model Transformations}

\subsection{Markov Blankets}

\subsection{Conditional Predictive models}

\subsection{Do}

\section{Symbolic Simplifcation}

\section{Code Generation}

@@

\todo[inline]{Let's implement models from \url{https://statisticalrethinkingjulia.github.io/MCMCBenchmarks.jl/latest/benchmarks/} for benchmark comparisons}

\todo[inline]{Can Soss really generate arbitrary code?}

The ability to generate arbitrary  Julia code makes it difficult to measure performance in Soss. When a performance bottleneck is found, developers or users can ask Soss to generate something different. This design places no a priori constraints on performance.

@@

\emph{Gen} \cite{Cusumano-Towner:2019} was developed independently from Soss, but takes a similar approach (and distinct from most PPLs) in its representation of a model as a function from its arguments to a "trace" (to use Gen's terminology). In both Soss and Gen's static DSL, this trace is a mapping from variable names to values. The similarity of these systems makes interoperability relatively straightforward, as demonstrated in \emph{SossGen}(\url{https://github.com/cscherrer/SossGen.jl}).

@@

\section{Model Syntax}
